
---
title: "Course Project Codebook"
author: "DoHo"
date: "21 Mai 2018"
output: html_document
---

This is the codebook accompanying and explaining the variables of the Tidydata.txt. This data was generated using the script run_analysis.R. 

Note: for better understanding the  variable names have been altered to be more readable. First, special characters  such as () and - have been removed.  Abbreviations are fully spelled  out, e.g: "Acc" -> "Accelerometer", "t" -> "time", etc. A typo "BodyBody" has been fixed to "Body".

The source of the data set is: https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip.

Information on the data set itself, quoted from source "http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones":
"Data Set Information:

The experiments have been carried out with a group of 30 volunteers within an age bracket of 19-48 years. Each person performed six activities (WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING) wearing a smartphone (Samsung Galaxy S II) on the waist. Using its embedded accelerometer and gyroscope, we captured 3-axial linear acceleration and 3-axial angular velocity at a constant rate of 50Hz. The experiments have been video-recorded to label the data manually. The obtained dataset has been randomly partitioned into two sets, where 70% of the volunteers was selected for generating the training data and 30% the test data.

The sensor signals (accelerometer and gyroscope) were pre-processed by applying noise filters and then sampled in fixed-width sliding windows of 2.56 sec and 50% overlap (128 readings/window). The sensor acceleration signal, which has gravitational and body motion components, was separated using a Butterworth low-pass filter into body acceleration and gravity. The gravitational force is assumed to have only low frequency components, therefore a filter with 0.3 Hz cutoff frequency was used. From each window, a vector of features was obtained by calculating variables from the time and frequency domain."


Steps that led  to the creation of Tidydata.txt:

    1. The training and the test sets were merged to create one data set.
    2. Only the measurements on the mean and standard deviation for each measurement were extracted.
    3. Descriptive activity names to name the activities in the data set are used.
    4. Appropriately labeled the data set with descriptive variable names.
    5. From the data set in step 4, a second, independent tidy data set (Tidydata.txt) was created with the average of each variable for each activity and each subject.
    
VARIABLES: 

1. Subjects
integer; People taking part in the tests. Range from 1 to 30.


2. Activities
character; Identifier denouncing what tasks the subjects performed during the tests:
```{r}
WALKING
WALKING_UPSTAIRS
WALKING_DOWNSTAIRS
SITTING
STANDING
LAYING
```
 
MEASUREMENTS and UNITS:

Measurements captured are body acceleration and angular velocity Note: Features are normalized and bounded within [-1,1].

Units before normalization: standard gravity units (9.81 m/s²) for measurement of body 
```{r}
Acceleration
```
values
and
radians/second (rd.s^-1) for measurement of angular velocity captured in
```{r}
Gyroscope
```
values.

Also, the
```{r}
magnitude
```
of these three-dimensional signals were calculated using the Euclidean norm.

The data set is parted in two domains, all signals are floating point numbers:

timeDomain values are results of the accelerometer and gyroscope 3-axial raw signals.

frequencyDomain signals are the results of a Fast Fourier Transform (FFT) being applied to some of the signals.

timeDomain Values:


Mean timeDomain body acceleration values for directions X, Y  and Z:

  timeDomainBodyAccelerometerMeanX
  timeDomainBodyAccelerometerMeanY
  timeDomainBodyAccelerometerMeanZ
    
Standard Deviation timeDomain body acceleration values for directions X, Y and Z:

   timeDomainBodyAccelerometerStandardDeviationX
   timeDomainBodyAccelerometerStandardDeviationY
   timeDomainBodyAccelerometerStandardDeviationZ
   
Mean timeDomain gravity acceleratiion values for directions X, Y and Z:

   timeDomainGravityAccelerometerMeanX
   timeDomainGravityAccelerometerMeanY
   timeDomainGravityAccelerometerMeanZ
   
Standard Deviation gravity acceleration for  directions X, Y and Z:

  timeDomainGravityAccelerometerStandardDeviationX
  timeDomainGravityAccelerometerStandardDeviationY
  timeDomainGravityAccelerometerStandardDeviationZ
  
Mean timeDomain acceleration Jerk signals for directions X, Y and Z: 

  timeDomainBodyAccelerometerJerkMeanX
  timeDomainBodyAccelerometerJerkMeanY
  timeDomainBodyAccelerometerJerkMeanZ
  
Standard Deviation timeDomain acceleration Jerk signals for directions X,  Y and Z:

  timeDomainBodyAccelerometerJerkStandardDeviationX
  timeDomainBodyAccelerometerJerkStandardDeviationY
  timeDomainBodyAccelerometerJerkStandardDeviationZ
  
Mean timeDomain body angular velocity signals for  directions X, Y and Z:

  timeDomainBodyGyroscopeMeanX
  timeDomainBodyGyroscopeMeanY
  timeDomainBodyGyroscopeMeanZ
  
Standard Deviation timeDomain body angular velocity signals for  directions X, Y and Z:

  timeDomainBodyGyroscopeStandardDeviationX
  timeDomainBodyGyroscopeStandardDeviationY
  timeDomainBodyGyroscopeStandardDeviationZ
  
Mean timeDomain body angular velocity Jerk signals for directions X, Y and Z: 
  
  timeDomainBodyGyroscopeJerkMeanX
  timeDomainBodyGyroscopeJerkMeanY
  timeDomainBodyGyroscopeJerkMeanZ
  
Standard Deviation timeDomain body angular velocity Jerk signals for directions X, Y and Z: 

  timeDomainBodyGyroscopeJerkStandardDeviationX
  timeDomainBodyGyroscopeJerkStandardDeviationY
  timeDomainBodyGyroscopeJerkStandardDeviationZ
  
Body acceleration Magnitude signals for Mean and Standard Deviation:

  timeDomainBodyAccelerometerMagnitudeMean
  timeDomainBodyAccelerometerMagnitudeStandardDeviation
  
Body angular velocity Magnitude signals for Mean and Standrd Deviation:

  timeDomainGravityAccelerometerMagnitudeMean
  timeDomainGravityAccelerometerMagnitudeStandardDeviation
  
Body acceleration Jerk Magnitude signals for Mean and Standard Deviation:

  timeDomainBodyAccelerometerJerkMagnitudeMean
  timeDomainBodyAccelerometerJerkMagnitudeStandardDeviation
  
Body angular velocity Magnitude signals for Mean and Standard Deviation:
  
  timeDomainBodyGyroscopeMagnitudeMean
  timeDomainBodyGyroscopeMagnitudeStandardDeviation
  
Body angular velocity Jerk Magnitude signals for Mean and  Standard Deviation:
  
  timeDomainBodyGyroscopeJerkMagnitudeMean
  timeDomainBodyGyroscopeJerkMagnitudeStandardDeviation
  


frequencyDomain Values:
   
Mean frequencyDomain body acceleration values for directions X, Y  and Z:

  frequencyDomainBodyAccelerometerMeanX
  frequencyDomainBodyAccelerometerMeanY
  frequencyDomainBodyAccelerometerMeanZ
             
Standard Deviation frequencyDomain body acceleration values for directions X, Y and Z:
             
  frequencyDomainBodyAccelerometerStandardDeviationX
  frequencyDomainBodyAccelerometerStandardDeviationY
  frequencyDomainBodyAccelerometerStandardDeviationZ
             
Mean frequencyDomain acceleration Jerk signals for directions X, Y and Z: 
             
  frequencyDomainBodyAccelerometerJerkMeanX
  frequencyDomainBodyAccelerometerJerkMeanY
  frequencyDomainBodyAccelerometerJerkMeanZ
             
Standard Deviation frequencyDomain acceleration Jerk signals for directions X,  Y and Z:
             
  frequencyDomainBodyAccelerometerJerkStandardDeviationX
  frequencyDomainBodyAccelerometerJerkStandardDeviationY
  frequencyDomainBodyAccelerometerJerkStandardDeviationZ
             
Mean frequencyDomain body angular velocity signals for  directions X, Y and Z:
             
  frequencyDomainBodyGyroscopeMeanX
  frequencyDomainBodyGyroscopeMeanY
  frequencyDomainBodyGyroscopeMeanZ
             
Standard Deviation frequencyDomain body angular velocity signals for  directions X, Y and Z:
             
  frequencyDomainBodyGyroscopeStandardDeviationX
  frequencyDomainBodyGyroscopeStandardDeviationY
  frequencyDomainBodyGyroscopeStandardDeviationZ
             
Body acceleration Magnitude signals for Mean and Standard Deviation:
             
  frequencyDomainBodyAccelerometerMagnitudeMean
  frequencyDomainBodyAccelerometerMagnitudeStandardDeviation
             
Body angular velocity Magnitude signals for Mean and Standrd Deviation:
             
  frequencyDomainGravityAccelerometerMagnitudeMean
  frequencyDomainGravityAccelerometerMagnitudeStandardDeviation
             
Body acceleration Jerk Magnitude signals for Mean and Standard Deviation:
             
  frequencyDomainBodyAccelerometerJerkMagnitudeMean
  frequencyDomainBodyAccelerometerJerkMagnitudeStandardDeviation
             
Body angular velocity Magnitude signals for Mean and Standard Deviation:
             
  frequencyDomainBodyGyroscopeMagnitudeMean
  frequencyDomainBodyGyroscopeMagnitudeStandardDeviation
             
Body angular velocity Jerk Magnitude signals for Mean and  Standard Deviation:
             
  frequencyDomainBodyGyroscopeJerkMagnitudeMean
  frequencyDomainBodyGyroscopeJerkMagnitudeStandardDeviation





